\chaptertoc{Abstract}

\lettrine[nindent=0em, slope=.5em] {\color{Eblue}T}{his} document presents a synthesis of our end-of-year project conducted at the training center \textbf{Code212}. This innovative \textbf{text classification} project focuses on developing a sentiment analysis application capable of analyzing and understanding emotions and opinions expressed in \textbf{Hespress} website comments.

\ \\

\lettrine[nindent=0em, slope=.5em] {\color{Eblue}T}{he} project involves designing and implementing a sophisticated \textbf{text classification} web application for sentiment analysis that utilizes a modern architecture with \textbf{Next.js} for the frontend, \textbf{FastAPI} for the backend, \textbf{Keycloak} for authentication, \textbf{Selenium} for web scraping Hespress comments, the \textbf{cardiffnlp/twitter-xlm-roberta-base-sentiment} model for text classification, and \textbf{Spring Cloud Gateway} as API gateway. The application automatically extracts Hespress comments and provides detailed analysis of their sentiment, categorizing texts as positive, negative, or neutral.

\ \\

\lettrine[nindent=0em, slope=.5em] {\color{Eblue}T}{he} application incorporates advanced \textbf{Natural Language Processing} technologies and machine learning with the pre-trained cardiffnlp model to ensure precise and nuanced analysis of Hespress comments. It provides a modern user interface developed with Next.js for visualizing analysis results through graphs and detailed reports, facilitating the understanding of emotional trends in extracted comments.

\ \\

\lettrine[nindent=0em, slope=.5em] {\color{Eblue}T}{o} manage this project effectively, we adopted the \textbf{SCRUM} methodology and divided the work into sprints. Sprint 1 was dedicated to environment configuration and model integration. Sprint 2 focused on developing web scraping with Selenium and data preprocessing. Sprint 3 concentrated on dashboard development with Next.js and authentication interface with Keycloak. Finally, Sprint 4 completed report generation, optimization and deployment with Spring Cloud Gateway.

\ \\

\lettrine[nindent=0em, slope=.5em] {\color{Eblue}I}{n} summary, our sentiment analysis application developed for the Code212 training center represents an innovative \textbf{text classification} solution for automatically understanding and analyzing emotions expressed in Hespress website comments. It combines modern technologies like Next.js, FastAPI, Keycloak, Selenium and the cardiffnlp model with a microservices architecture using Spring Cloud Gateway, offering a powerful tool for opinion and sentiment analysis in news comments.
